---
title: "20211213_NifaMaps"
author: "Jose Dias"
date: "12/13/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# R Setup
```{r}
rm(list=ls(all=T)) # erase the GLOBAL ENVIRONMENT
#knitr::opts_chunk$set(echo=TRUE, comment=NA)
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
```


<!--- Load libraries and process data for plotting -->
```{r libraries, echo=FALSE, eval=TRUE, message=FALSE}
library(tidyverse)
# tidyverse_packages(include_self = FALSE)
# Loads: dplyr forcats ggplot2 lubridate purrr tibble

# For producing maps:
library(sf)
# NOTE: sf requires maptools, rgeos to be loaded

# Random forest fitting and tuning
library(caret)
library(ranger)
library(tuneRanger)
library(mlr)

# Feature importance
library(iml)

# For color schemes:
library(RColorBrewer)
library(ggsci)

# For graphics layout:
library(gridExtra)
library(grid)
library(gtable)

library(kableExtra)
library(rcompanion)
library(tidyverse)
library(sf)
library(here)
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)

#install.packages(c("cowplot", "googleway", "ggplot2", "ggrepel", 
#"ggspatial", "libwgeom", "sf", "rnaturalearth", "rnaturalearthdata"))

library(rnaturalearth)
library(rnaturalearthdata)
library(maps)
library("ggrepel")
library("ggspatial")

```


# Calling Dataset
```{r, include=FALSE}
# setting wd
getwd()
setwd('D/01.R/2022 Maps')
getwd()

alfalfa<-read.csv("20211213_MAPS.csv", header=TRUE, as.is=T, na.strings=".")         

anyNA(alfalfa)
colnames(alfalfa, do.NULL = TRUE, prefix = "col")
length(alfalfa$PLOT)
str(alfalfa)
summary(alfalfa)
```


# Getting Base Shape Files
```{r, include=FALSE}
options(digits = 3)
set.seed(1234)
theme_set(theme_minimal())

# Here we get a USA map from maps:
usa <- map_data("usa")
dim(usa)
head(usa)
tail(usa)

# Here is the high-res world map centered on the Pacific Ocean from mapdata
w2hr <- map_data("world2Hires")
dim(w2hr)
head(w2hr)
tail(w2hr)

################################################################################
states <- read_sf("D:/01.R/2020.04.13 RT NIFA/Shapefiles/cb_2018_us_state_500k/cb_2018_us_state_500k.shp")
states
head(states)
print(states, n = nrow(states))   # Print all rows of tibble

plot(states)

ggplot(data = states) +
  geom_sf()

################################################################################
counties <- read_sf("D:/01.R/2020.04.13 RT NIFA/Shapefiles/cb_2018_us_county_500k/cb_2018_us_county_500k.shp")
counties
head(counties)
tail(counties)

counties_48 <- counties %>%
  filter(!(STATEFP %in% c("15", "11", "60", "78", "69", "72", "66", "02")))
counties_48

ggplot(data = counties_48) +
  geom_sf()


################################################################################
# Florida with Counties
counties_48
counties_48b <- subset(counties_48, grepl("12", counties_48$STATEFP))
counties_48b
print(counties_48b, n = nrow(counties_48b))   # Print all rows of tibble


################################################################################
states2 <- as.data.frame(states)
states2

usa_48 <- states %>%
  filter(!(NAME %in% c("Hawaii", "District of Columbia", "American Samoa", "United States Virgin Islands", "Commonwealth of the Northern Mariana Islands", "Puerto Rico", "Guam", "Alaska")))
usa_48

plot(usa_48)

ggplot(data = usa_48) +
  geom_sf()

################################################################################
states_WI <- states %>%
  filter((NAME %in% c("Wisconsin")))
states_WI
plot(states_WI)

ggplot(data = states_WI) +
  geom_sf()

################################################################################
states_AZ <- states %>%
  filter((NAME %in% c("Arizona")))
states_AZ
plot(states_AZ)

ggplot(data = states_AZ) +
  geom_sf()

################################################################################
states_NIFA <- states %>%
  filter((NAME %in% c("Michigan", "Pennsylvania", "Wisconsin", "Idaho")))
states_NIFA
plot(states_NIFA)

ggplot(data = states_NIFA) +
  geom_sf()

################################################################################
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)
```

# Some Map types
```{r}
################################################################################
theme_set(theme_bw())

world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)

(sites <- data.frame(longitude = c(-80.144005, -80.109), latitude = c(26.479005, 
    26.83)))

ggplot(data = world) +
    geom_sf() +
    geom_point(data = sites, aes(x = longitude, y = latitude), size = 4, 
        shape = 23, fill = "darkred") +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)

(sites <- st_as_sf(sites, coords = c("longitude", "latitude"), 
    crs = 4326, agr = "constant"))

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = sites, size = 4, shape = 23, fill = "darkred") +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)

################################################################################
#states_3 <- st_as_sf(map("state", plot = TRUE, fill = TRUE))
head(usa_48)
usa_48

usa_48
usa_48b <- cbind(usa_48, st_coordinates(st_centroid(usa_48)))
usa_48b

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = usa_48b, fill = NA) + 
    geom_text(data = usa_48b, aes(X, Y, label = NAME), size = 5) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)

################################################################################
usa_48b$nudge_y <- -1
usa_48b$nudge_y[usa_48b$NAME == "Florida"] <- 0.5
usa_48b$nudge_y[usa_48b$NAME == "South Carolina"] <- -1.5

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = usa_48b, fill = NA) + 
    geom_label(data = usa_48b, aes(X, Y, label = NAME), size = 5, fontface = "bold", 
        nudge_y = usa_48b$nudge_y) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)

################################################################################
counties_48
counties_48b <- subset(counties_48, grepl("12", counties_48$STATEFP))
counties_48b
print(counties_48b, n = nrow(counties_48b))   # Print all rows of tibble

counties_48b$area <- as.numeric(st_area(counties_48b))
head(counties_48b)

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = counties_48b, fill = NA, color = gray(.5)) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)

################################################################################
# We can also fill in the county using their area to visually identify the largest counties. For this, we use the “viridis” colorblind-friendly palette, with some transparency:

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = counties_48b, aes(fill = area)) +
    scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)


################################################################################
# Cities (point data)
#To make a more complete map of Florida, main cities will be added to the map. We first prepare a data frame with the five largest cities in the state of Florida, and their geographic coordinates:

flcities <- data.frame(state = rep("Florida", 5), city = c("Miami", 
    "Tampa", "Orlando", "Jacksonville", "Sarasota"), lat = c(25.7616798, 
    27.950575, 28.5383355, 30.3321838, 27.3364347), lng = c(-80.1917902, 
    -82.4571776, -81.3792365, -81.655651, -82.5306527))

# We can now convert the data frame with coordinates to sf format:
(flcities <- st_as_sf(flcities, coords = c("lng", "lat"), remove = FALSE, 
    crs = 4326, agr = "constant"))


# We add both city locations and names on the map:
ggplot(data = world) +
    geom_sf() +
    geom_sf(data = counties_48b, fill = NA, color = gray(.5)) +
    geom_sf(data = flcities) +
    geom_text(data = flcities, aes(x = lng, y = lat, label = city), 
        size = 3.9, col = "black", fontface = "bold") +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)

# This is not really satisfactory, as the names overlap on the points, and they are not easy to read on the grey background. The package ggrepel offers a very flexible approach to deal with label placement (with geom_text_repel and geom_label_repel), including automated movement of labels in case of overlap. We use it here to “nudge” the labels away from land into the see, and connect them to the city locations:
library("ggrepel")
ggplot(data = world) +
    geom_sf() +
    geom_sf(data = counties_48b, fill = NA, color = gray(.5)) +
    geom_sf(data = flcities) +
    geom_text_repel(data = flcities, aes(x = lng, y = lat, label = city), 
        fontface = "bold", nudge_x = c(1, -1.5, 2, 2, -1), nudge_y = c(0.25, 
            -0.25, 0.5, 0.5, -0.5)) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE)
```


# Final Map
`For the final map, we put everything together, having a general background map based on the world map, with state and county delineations, state labels, main city names and locations, as well as a theme adjusted with titles, subtitles, axis labels, and a scale bar:`

```{r}
library("ggspatial")

# Florida color by county area
ggplot(data = world) +
    geom_sf(fill = "antiquewhite1") +
    geom_sf(data = counties_48b, aes(fill = area)) +
    geom_sf(data = usa_48b, fill = NA) + 
    geom_sf(data = sites, size = 4, shape = 23, fill = "darkred") +
    geom_sf(data = flcities) +
    geom_text_repel(data = flcities, aes(x = lng, y = lat, label = city), 
        fontface = "bold", nudge_x = c(1, -1.5, 2, 2, -1), nudge_y = c(0.25, 
            -0.25, 0.5, 0.5, -0.5)) +
    geom_label(data = usa_48b, aes(X, Y, label = NAME), size = 5, fontface = "bold", 
        nudge_y = usa_48b$nudge_y) +
    scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
    annotation_scale(location = "bl", width_hint = 0.4) +
    annotation_north_arrow(location = "bl", which_north = "true", 
        pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_fancy_orienteering) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE) +
    xlab("Longitude") + ylab("Latitude") +
    ggtitle("Observation Sites", subtitle = "(2 sites in Palm Beach County, Florida)") +
    theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))

# Florida different color than the other states
ggplot(data = world) +
    geom_sf(fill = "antiquewhite1") +
    geom_sf(data = counties_48b, fill = "red") +
    geom_sf(data = usa_48b, fill = NA) + 
    geom_sf(data = sites, size = 4, shape = 23, fill = "darkred") +
    geom_sf(data = flcities) +
    geom_text_repel(data = flcities, aes(x = lng, y = lat, label = city), 
        fontface = "bold", nudge_x = c(1, -1.5, 2, 2, -1), nudge_y = c(0.25, 
            -0.25, 0.5, 0.5, -0.5)) +
    geom_label(data = usa_48b, aes(X, Y, label = NAME), size = 5, fontface = "bold", 
        nudge_y = usa_48b$nudge_y) +
    scale_fill_viridis_c(trans = "sqrt", alpha = .4) +
    annotation_scale(location = "bl", width_hint = 0.4) +
    annotation_north_arrow(location = "bl", which_north = "true", 
        pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_fancy_orienteering) +
    coord_sf(xlim = c(-88, -78), ylim = c(24.5, 33), expand = FALSE) +
    xlab("Longitude") + ylab("Latitude") +
    ggtitle("Observation Sites", subtitle = "(2 sites in Palm Beach County, Florida)") +
    theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))

```



# Cool ML Paper / Soybean
## By Year 01
<!-- Supplementary Figure S1 -->
```{r FieldLocations-MG, eval=TRUE, echo=FALSE}
################################################################################
# Locations of all the fields facetted by year, field locations colored by maturity group:
ggplot() +
  geom_sf(data=usa_48) +
  geom_sf(data = states_NIFA, fill = "antiquewhite1") +
  theme_bw() +
  geom_point(data = alfalfa, aes(x = Longitude, y = Latitude, colour = Texture2), size = 1.5, alpha = 0.5) +
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ Year, nrow = 2) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 9, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 9),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold", size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "Maturity group", override.aes = list(alpha = 1)))
```

## By Year 02
<!-- Supplementary Figure S1 -->
```{r FieldLocations-MG, eval=TRUE, echo=FALSE}
################################################################################
ggplot() +
  geom_sf(data=usa_48) +
  geom_sf(data = states_NIFA, fill = "antiquewhite1") +
  theme_bw() +
  geom_point(data = alfalfa, aes(x = Longitude, y = Latitude, colour = Texture2, shape = CornRM_Class), size = 1.75, alpha = 0.5) +
  #geom_sf(data = alfalfa_SF, size = 2, shape = 23) +
  coord_sf(xlim = c(-70, -125), ylim = c(37, 50), expand = FALSE) + 
  scale_color_brewer(type = "qual", palette = "Set1", direction = 1) +
  facet_wrap(~ Year, nrow = 2) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(axis.title.x = element_text(face = "bold", size = 12),
        axis.text.x  = element_text(size = 9, angle = 90),
        axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
        axis.text.y  = element_text(size = 9),
        # Bold the facet text labels:
        strip.text = element_text(face = "bold", size = 10)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
  # override the transparency of the points for the legend:
  guides(colour = guide_legend(nrow = 1, title = "Topsoil texture", override.aes = list(alpha = 1))) + 
    guides(shape = guide_legend(nrow = 1, title = "Corn Maturity group", override.aes = list(alpha = 1)))


```

```{r}
################################################################################
alfalfa

alfalfa_points <- alfalfa %>% select(Latitude, Longitude)
alfalfa_points

ggplot(data = world) +
    geom_sf() +
    geom_point(data = alfalfa_points, aes(x = Longitude, y = Latitude), size = 4, 
        shape = 23, fill = "darkred") +
    coord_sf(xlim = c(-75, -125), ylim = c(34, 50), expand = FALSE)

################################################################################
alfalfa_SF <- st_as_sf(alfalfa_points, coords = c("Longitude", "Latitude"), 
    crs = 4326, agr = "constant")
alfalfa_SF

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = alfalfa_SF, size = 4, shape = 23, fill = "darkred") +
    coord_sf(xlim = c(-75, -125), ylim = c(34, 50), expand = FALSE)

################################################################################
states_NIFA
states_NIFAb <- cbind(states_NIFA, st_coordinates(st_centroid(states_NIFA)))
states_NIFAb

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = usa_48b, fill = NA) + 
    geom_text(data = states_NIFAb, aes(X, Y, label = NAME), size = 5) +
    coord_sf(xlim = c(-75, -125), ylim = c(34, 50), expand = FALSE)

################################################################################
states_NIFAb$nudge_y <- -1
states_NIFAb$nudge_y[states_NIFAb$NAME == "Michigan"] <- 1.5
states_NIFAb$nudge_y[states_NIFAb$NAME == "Pennsylvania"] <- 2
states_NIFAb$nudge_y[states_NIFAb$NAME == "Wisconsin"] <- 2.75
states_NIFAb$nudge_y[states_NIFAb$NAME == "Idaho"] <- 2.5

ggplot(data = world) +
    geom_sf() +
    geom_sf(data = usa_48b, fill = NA) + 
    geom_sf(data = states_NIFAb, fill = "antiquewhite1") + 
    geom_label(data = states_NIFAb, aes(X, Y, label = NAME), size = 3, fontface = "bold", 
        nudge_y = states_NIFAb$nudge_y) +
    coord_sf(xlim = c(-70, -125), ylim = c(37, 50), expand = FALSE)



```

#
```{r}
library(sf)
library(ggplot2)
library(dplyr)

# Contiguous US state boundaries
usa = st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))

# Simulate some random points
pts = data.frame(
  x = c(-91.6, -74.3, -101.5),
  y = c(36.1, 42.1, 25.3)
  ) %>%
  st_as_sf(coords=c("x", "y"), crs = 4326)

ggplot() +
  geom_sf(data = usa, fill = NA) +
  geom_sf(data = pts,
          shape = 21, size = 4, fill = "red") +
  coord_sf(crs = st_crs(102003)) +
  theme_minimal()
```

# Polygon maps

## 
```{r}
mi_counties <- map_data("county", "michigan") %>% 
  select(lon = long, lat, group, id = subregion)
head(mi_counties)
```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```

##
```{r}

```






















